---
title: "Weight of Fish"
author: "David Barton"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species)
```


### Best Models

```{r}
Perchmodel1<- lm(Weight~ .,data=Perch)
summary.lm(Perchmodel1)
```

### Best Two regressor model




```{r}
library(leaps)
Perchmodel1automate <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Perch <- summary(Perchmodel1automate)
as.data.frame(summary.Perch$outmat)
library(car)
subsets(Perchmodel1automate,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```


After running this code, I found the best single element regression model (Height), the best 2 element regression models (Height and Width), and I was also able to get the best 3,4 and 5 elements regression


## Pike

```{r}
Pikemodel1<- lm(Weight~ .,data=Perch)
summary.lm(Pikemodel1)
```

### Best Models

```{r}
library(leaps)
Pikemodel1automate <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Pike <- summary(Pikemodel1automate)
as.data.frame(summary.Pike$outmat)
library(car)
subsets(Pikemodel1automate,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

 
 After running code. I was able to see that the code for the pike was best at regression models were length 1&3. The best regression models were Length 1,2,3 as well as height and width. The complete model. All jugded based off the r-square vaule. 
 
 
### Best Two regressor model

## Roach

```{r}
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
```


### Best Models

```{r}
library(leaps)
Roachmodel1automate <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Roach <- summary(Pikemodel1automate)
as.data.frame(summary.Pike$outmat)
library(car)
subsets(Roachmodel1automate,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



After running the code. It was clear to see the 5 regressor models. The best 2 regressor models and the best model was lenght 3 and width. 
### Best Two regressor model

## Final Summary Statements

In this assignment. I was tasked to compare the regessions models of the different types of the fish. I had to compare the weight and length and the width of these fishes: The Roach, Pike, and Perch. I was estimated the weight and length and the width. I was made to use the adjusted R-square value to get the best 2 element regressor. For the perch the best was height and the width. for the pike it was the length and the width, and lastly, for the roach it weight and length.




